%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Related Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Lixar IT} % Organization
    {Halifax, Nova Scotia [Remote]} % Location
    {Aug. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	% \item {Led team of 3+ other software developers to implement web application using \cvitemskill{JavaScript}, \cvitemskill{Sass}, \cvitemskill{React.js}, \cvitemskill{Node.js}, \cvitemskill{Docker}, \cvitemskill{Webpack}.}
  \item {Redesigned build process with \cvitemskill{TeamCity}, \cvitemskill{Git}, \cvitemskill{Docker}, \cvitemskill{Node.js}, and \cvitemskill{Webpack}, reducing build time from \approx 60 minutes to \approx 20 minutes.}
  \item {Improved API response time from 30-120 seconds to consistent sub-second measurements using \cvitemskill{Redis}, \cvitemskill{Node.js}, \cvitemskill{TypeScript}, \cvitemskill{GraphQL}.}
  % \item {Improved unit \& integration testing coverage using \cvitemskill{Mocha}, and added acceptance testing with \cvitemskill{Gherkin} and \cvitemskill{Cucumber.js}.}
  \item {Fixed defects in critical software while preventing regressions using \cvitemskill{Mocha} for unit/integration \& \cvitemskill{Gherkin} with \cvitemskill{Cucumber.js} for acceptance tests.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Full-Stack Software Developer} % Job title
    {Freelancing} % Organization
    {Dartmouth, Nova Scotia [Remote]} % Location
    {May 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led team of 2+ other software developers to design and develop iOS application with \cvitemskill{React Native} and \cvitemskill{GraphQL} API server with \cvitemskill{\href{https://www.reindex.io/}{Reindex}}.}
        \item {Developed web application and \cvitemskill{GraphQL} API server with \cvitemskill{React.js}, \cvitemskill{Relay}, \cvitemskill{Node.js}, \cvitemskill{\href{https://github.com/serverless/serverless}{Serverless}} framework, and \cvitemskill{AWS}'s \cvitemskill{DynamoDB}.}
        \item {Developed Slack Bot using \cvitemskill{Wit.ai}, \cvitemskill{Botkit}, and \cvitemskill{Node.js} integrating with existing API for data retrieval.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant (Honours Student)} % Job title
    {Saint Mary's University} % Organization
    {Halifax, Nova Scotia} % Location
    {Jan. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented classification and clustering research of electroencephalogram (EEG) data in \cvitemskill{R} and \cvitemskill{Java} using methods \cvitemskill{Decision Tree}, \cvitemskill{Random Forest}, \cvitemskill{Support Vector Machines (SVM)}, \cvitemskill{Neural Networks}, and \cvitemskill{Genetic Algorithms}.}
        \item {Co-authored two conference papers and a book chapter written with \cvitemskill{LaTeX}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Skilltapper} % Organization
    {Lakeville, New Brunswick [Remote]} % Location
    {Jul. 2015 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 3 other software developers \cvitemskill{remotely}, using \cvitemskill{Google Hangouts} for Video Calling and \cvitemskill{GitHub}'s Issue Tracker.}
        \item {Developed web application in \cvitemskill{JavaScript} using \cvitemskill{Ember.js} framework and \cvitemskill{Sass}.}
        \item {Developed a \cvitemskill{RESTful API} server in \cvitemskill{Node.js} using \cvitemskill{Sails.js} framework to interact with customer data stored in \cvitemskill{MongoDB} and \cvitemskill{Redis}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cofounder, Vice President of Engineering} % Job title
    {Streamlyne Technologies}  % Organization
    {Dartmouth, Nova Scotia} % Location
    {Apr. 2013 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Co-led and mentored a team of 4 other software developers, using \cvitemskill{GitHub}'s Issue Tracker and \cvitemskill{pair programming}.}
  \item {Designed and implemented rule engine to process >5,000 sensors/second using \cvitemskill{Redis}, \cvitemskill{RabbitMQ}, \cvitemskill{MongoDB}, \cvitemskill{Python}, \cvitemskill{Java}, \cvitemskill{AWS}.}
	\item {Designed and implemented the \cvitemskill{RESTful API} server with \cvitemskill{Python}, \cvitemskill{MongoDB}, \cvitemskill{Redis}, \cvitemskill{RabbitMQ}, \cvitemskill{AWS}.}
	\item {Developed web application in \cvitemskill{JavaScript} using \cvitemskill{Ember.js} framework, \cvitemskill{Ember Data}, and \cvitemskill{Sass}.}
%	\item {Developed \cvitemskill{iOS} application in \cvitemskill{Objective-C} for iPhone, iPod Touch, and iPad.}
	% \item {Collaborated with Data Scientist (Ph.D candidate) to design and implement predictive analytics system using \cvitemskill{R}, \cvitemskill{MongoDB}, and \cvitemskill{InfluxDB}.}
	% \item {Gained business \cvitemskill{presentation} experience by attending business meetings as technical representative along with sales representative.}
%	\item {Gained \cvitemskill{customer development} experience by working closely with early adopter customers to ensure their ideas and concerns were being heard and addressed with the Streamlyne technology.}
%	\item {Gained business-to-business software integration experience by working with third-party technical teams.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Compilr (Acquired by lynda.com)} % Organization
    {Halifax, Nova Scotia} % Location
    {May 2013 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Developed interactive source code recording web application for educators using \cvitemskill{JavaScript}, \cvitemskill{HTML}, \cvitemskill{CSS}, \cvitemskill{PHP}, \cvitemskill{Node.js}, and \cvitemskill{MySQL}.}
%	\item {Compilr was acquired by an online education company, Lynda.com, on April 7, 2014 and Compilr's education tools were integrated in Lynda.com's web application.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
