%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

% ===== Software Development ========
\begin{parcolumns}[colwidths={1=.1\textwidth},rulebetween=false]{2}
\colchunk{% left column
    \entrytitlestyle{
    Software\\ Development\\ Skills
    }
}
\colchunk{% right column
    \descriptionstyle{
    \vspace{-5mm} % Eliminate space before itemize 
    \begin{itemize}[noitemsep,topsep=0pt]
        		% Languages, Frameworks, Libraries
		% Front-end
		\item {Proficient developing front-end web applications with \cvitemskill{HTML5}, \cvitemskill{CSS3} (including \cvitemskill{LESS} and \cvitemskill{Sass}), \cvitemskill{JavaScript} (including \cvitemskill{ES6}), and \cvitemskill{CoffeeScript}, and using frameworks such as \cvitemskill{Bootstrap 3}, \cvitemskill{Ember.js}, and \cvitemskill{Angular.js} and libraries such as \cvitemskill{jQuery}, \cvitemskill{Lodash}/\cvitemskill{Underscore}, and \cvitemskill{Async}.}
%		\item {Developed \cvitemskill{iOS} application in \cvitemskill{Objective-C} for iPhone, iPod Touch, and iPad.}
		% Back-end
		\item {Proficient developing RESTful and WebSocket API back-ends in \cvitemskill{Node.js} and \cvitemskill{Python}, using frameworks such as \cvitemskill{Express}, \cvitemskill{Sails.js}, \cvitemskill{Loopback.io}, and \cvitemskill{Flask}, and using libraries such as \cvitemskill{Socket.io}, \cvitemskill{Lodash}/\cvitemskill{Underscore}, and \cvitemskill{Async}, and deploying with \cvitemskill{Amazon Web Services (AWS)}.}
		% Databases
		\item {Proficient designing data models for client-server applications with databases such as \cvitemskill{MongoDB} and \cvitemskill{MySQL}, along with using \cvitemskill{RabbitMQ} and \cvitemskill{Redis}.}
		% Testing & Continuous Integration
		\item {Experience with \cvitemskill{Test-Driven Development (TDD)} and using \cvitemskill{Continuous Integration} services, such as \cvitemskill{Travis CI} for Mac or Linux and \cvitemskill{AppVeyor} for Windows. for both corporate and open-source projects.}
        \end{itemize}
    }
}
\end{parcolumns}

% ===== Analytical ========
%\begin{parcolumns}[colwidths={1=.1\textwidth},rulebetween=false]{2}
%\colchunk{% left column
%    \entrytitlestyle{
%    Analytical\\ Skills
%    }
%}
%\colchunk{% right column
%    \descriptionstyle{
%    \vspace{-5mm} % Eliminate space before itemize 
%        \begin{itemize}
%            \item {Researched classification and clustering techniques, such as \cvitemskill{Decision Tree}, \cvitemskill{Random Forest}, \cvitemskill{Support Vector Machines (SVM)}, \cvitemskill{Neural Networks}, and \cvitemskill{Genetic Algorithms}, for classifying electroencephalogram (EEG) data based on person and activity.}
%            \item {Collaborated with experienced Data Scientist (Ph.D candidate) to design and implement predictive analytics system using \cvitemskill{R}, \cvitemskill{MongoDB}, and \cvitemskill{InfluxDB}.}
%        \end{itemize}
%    }
%}
%\end{parcolumns}

% ===== Communication ========
\begin{parcolumns}[colwidths={1=.1\textwidth},rulebetween=false]{2}
\colchunk{% left column
    \entrytitlestyle{
    Communication\\ Skills
    }
}
\colchunk{% right column
    \descriptionstyle{
    \vspace{-5mm} % Eliminate space before itemize 
        \begin{itemize}
	\item {Gained business \cvitemskill{presentation} experience by attending business meetings as technical representative along with sales representative of Streamlyne.}
	\item {Gained \cvitemskill{customer development} experience by working closely with early adopter customers to ensure their ideas and concerns were being heard and addressed with the Streamlyne technology.}
	\item {Gained \cvitemskill{writing technical documents}, such as for National Research Council's Industrial Research Assistance Program (NRC-IRAP) and Scientific Research and Experimental Development (SR\&ED) for Streamlyne.}
	\item {Gained business-to-business software integration experience by working with third-party technical teams.}
%        \item {Assisted with writing research papers in \cvitemskill{LaTeX}.}
        \end{itemize}
         \vspace*{-\baselineskip}\leavevmode
    }
}
\end{parcolumns}

% ===== Leadership ========
\begin{parcolumns}[colwidths={1=.1\textwidth},rulebetween=false]{2}
\colchunk{% left column
    \entrytitlestyle{
    Leadership\\ Skills
    }
}
\colchunk{% right column
    \descriptionstyle{
    \vspace{-5mm} % Eliminate space before itemize 
        \begin{itemize}
        	\item {Managed small teams of software developers at both Skilltapper and Streamlyne, both in office and remotely (\cvitemskill{telecommuting}) using \cvitemskill{Google Hangouts} for Video Calling and \cvitemskill{GitHub}'s Issue Tracker.}
	\item {Mentored students at Saint Mary's University while being Vice President of the Saint Mary's University Computing Science and Mathematics Society (SMUCSM).}
	\item {Assisted with hosting of \href{http://cs.smu.ca/hackaweek/}{Saint Mary's University's annual "Hack-A-Week" Hackathons}. }
	\item {Assisted with hosting \href{http://aigicrv.org/aigicrv2015/}{AI/GI/CRV 2015 Conference at Saint Mary's University and Dalhousie University}. }
        \end{itemize}
    }
}
\end{parcolumns}

%% ===== Teamwork ========
%\begin{parcolumns}[colwidths={1=.1\textwidth},rulebetween=false]{2}
%\colchunk{% left column
%    \entrytitlestyle{
%    Teamwork\\ Skills
%    }
%}
%\colchunk{% right column
%    \descriptionstyle{
%    \vspace{-5mm} % Eliminate space before itemize 
%        \begin{itemize}
%        	\item {Collaborated with small teams of software developers at Skilltapper, Streamlyne, Compilr, and open-source projects on \cvitemskill{GitHub}}
%        \end{itemize}
%    }
%}
%\end{parcolumns}


%---------------------------------------------------------
